---
title: "Question 2"
output: md_document
---

```{r, echo=FALSE, message=FALSE}
library(mosaic)
library(FNN)
library("foreach")
sclass <- read.csv("~/Desktop/sclass.csv")
sclass550 = subset(sclass, trim == '350')
dim(sclass550)
sclass65AMG = subset(sclass, trim == '65 AMG')
plot(price ~ mileage, data = sclass550)
plot(price ~ mileage, data = sclass65AMG)
```
By drawing the scatter plot, we can see the basic relationship between mileage and the price.
Concentrating on the data of sclass 550, and then make the train and test split, and we set the number of train set as the 80% of the whole data set, and the test set is the left ones.
Also, we concentrate on the data of sclass550 first.
```{r, echo=FALSE}
N = nrow(sclass550)
N_train = floor(0.8*N)
N_test = N - N_train
train_ind = sample.int(N, N_train, replace=FALSE)
D_train = sclass550[train_ind,]
D_test = sclass550[-train_ind,]
D_test = arrange(D_test, mileage)
head(D_test)
X_train = select(D_train, mileage)
y_train = select(D_train, price)
X_test = select(D_test, mileage)
y_test = select(D_test, price)
lm1 = lm(price ~ mileage, data=D_train)
lm2 = lm(price ~ poly(mileage, 2), data=D_train)
rmse = function(y, ypred) {
  sqrt(mean(data.matrix((y-ypred)^2)))
}
ypred_lm1 = predict(lm1, X_test)
ypred_lm2 = predict(lm2, X_test)
rmse(y_test, ypred_lm1)
rmse(y_test, ypred_lm2)
D_test$ypred_lm2 = ypred_lm2
N = nrow(sclass550)
N_train = floor(0.8*N)
N_test = N - N_train
train_ind = sort(sample.int(N, N_train, replace=FALSE))
D_train = sclass[train_ind,]
D_train = arrange(D_train, mileage)
y_train = D_train$price
X_train = data.frame(mileage=jitter(D_train$mileage))
knn_model = knn.reg(X_train, X_train, y_train, k = 3)
D_train$ypred = knn_model$pred
p_train = ggplot(data = D_train) + 
  geom_point(mapping = aes(x = mileage, y = price), color='lightgrey') + 
  theme_bw(base_size=18)
p_train + geom_path(mapping = aes(x=mileage, y = ypred), color='red', size=1.5)
```
And then we can draw the graph for the relationship between mileage and the price by taking K=3 first.
```{r, echo=FALSE}
k_grid1 = unique(round(exp(seq(log(330),log(3),length=100))))
rmse_grid_in1=foreach(k=k_grid1, .combine='c') %do% {
  knn_model1_2 = knn.reg(X_train, X_train, as.data.frame(y_train), k = k)
  rmse(y_train, knn_model1_2$pred)
}

rmse_grid_in1 = data.frame(K = k_grid1, RMSE = rmse_grid_in1)

ggplot(data = rmse_grid_in1) + 
  geom_line(mapping = aes(x = K, y = RMSE))
```
And by calculating the RMSE under different K value, we can generally draw a graph for the K value and the RMSE for in-sample data.
And then we can draw a graph indicating the relationship between the K and RMSE for the out of sample.
```{r, echo=FALSE}
k_grid3 = unique(round(exp(seq(log(30),log(3),length=10))))
rmse_grid_in3=foreach(k=k_grid3, .combine='c') %do% {
  knn_model1_3 = knn.reg(X_test, X_test, y_train, k = k)
  rmse(y_test, knn_model1_3$pred)
}
rmse_grid_in3 = data.frame(K = k_grid3, RMSE = rmse_grid_in3)
ind_best = which.min(rmse_grid_in3$RMSE)
k_best = k_grid1[ind_best]
k_best
```
After that, we move on to another part of dataset as data refers to sclass65AGM.And conducting the similar process as above.
```{r, echo=FALSE}
N = nrow(sclass65AMG)
N_train = floor(0.8*N)
N_test = N - N_train
train_ind = sample.int(N, N_train, replace=FALSE)
D_train_1 = sclass65AMG[train_ind,]
D_test_1 = sclass65AMG[-train_ind,]
D_test_1 = arrange(D_test_1, mileage)
head(D_test_1)
X_train_1 = select(D_train_1, mileage)
y_train_1 = select(D_train_1, price)
X_test_1 = select(D_test_1, mileage)
y_test_1 = select(D_test_1, price)
lm11 = lm(price ~ mileage, data=D_train_1)
lm22 = lm(price ~ poly(mileage, 2), data=D_train_1)
rmse = function(y, ypred) {
  sqrt(mean(data.matrix((y-ypred)^2)))
}
p_test = ggplot(data = D_test_1) + 
  geom_point(mapping = aes(x = mileage, y = price), color='lightgrey') + 
  theme_bw(base_size=18) 
p_test
```
Here is a scatter plot of the relationship between mileage and the price.
```{r, echo=FALSE}
N = nrow(sclass65AMG)
N_train = floor(0.8*N)
N_test = N - N_train
train_ind = sort(sample.int(N, N_train, replace=FALSE))
D_train_1 = sclass[train_ind,]
D_train_1 = arrange(D_train_1, mileage)
y_train_1 = D_train_1$price
X_train_1 = data.frame(mileage=jitter(D_train_1$mileage))
```
Now we can firstly draw a relationship between miles and prices under the condition K=3
```{r, echo=FALSE}
knn_model = knn.reg(X_train_1, X_train_1, y_train_1, k = 3)
D_train_1$ypred = knn_model$pred
p_train_1 = ggplot(data = D_train_1) + 
  geom_point(mapping = aes(x = mileage, y = price), color='lightgrey') + 
  theme_bw(base_size=18)
p_train + geom_path(mapping = aes(x=mileage, y = ypred), color='red', size=1.5)
```
And then generally draw the graph for RMSE under different values of K,we generally assume the K value is from 0 to 30.
```{r, echo=FALSE}
k_grid2 = unique(round(exp(seq(log(30),log(3),length=10))))
rmse_grid_in2=foreach(k=k_grid2, .combine='c') %do% {
  knn_model1_3 = knn.reg(X_train_1, X_train_1, as.data.frame(y_train_1), k = k)
  rmse(y_train_1, knn_model1_3$pred)
}
rmse_grid_in2 = data.frame(K = k_grid2, RMSE = rmse_grid_in2)
ggplot(data = rmse_grid_in2) + 
  geom_line(mapping = aes(x = K, y = RMSE))
```
And for the our of sample, the result of relationship of K and RMSE is here.
```{r, echo=FALSE}
k_grid4 = unique(round(exp(seq(log(30),log(3),length=10))))
rmse_grid_in4=foreach(k=k_grid4, .combine='c') %do% {
  knn_model1_4 = knn.reg(X_train_1, X_test, as.data.frame(y_train_1), k = k)
  rmse(y_test, knn_model1_4$pred)
}
rmse_grid_in4 = data.frame(K = k_grid4, RMSE = rmse_grid_in4)
ind_best = which.min(rmse_grid_in4$RMSE)
k_best = k_grid4[ind_best]
k_best
ggplot(data = rmse_grid_in4) + 
  geom_line(mapping = aes(x = K, y = RMSE))
```
And for the optimal K, we can see that for the out of sample data, the relationship between K and RMSE generally depends on the K optimal value, which changes over the loop. In this way, we can not receive the optimal K value in the end. But by seeing the graphs, we can choose a relatively good value of K.